*Platynereis dumerilii* three-day-old connectome --- cell-type compendium

### 2024-10-21 supplements/celltype_compendium_website/index.qmd
cell type compendium webpage: separate code to generate RGL html viws from webpage rendering in index.qmd upload RGL views

plot_background <- function(x){
  nopen3d() # opens a pannable 3d window
  par3d(windowRect = c(0, 0, 200, 200)) #resize for frontal view
  plot3d(bounding_dots, add=T, col="white") 
  plot3d(yolk, add=T, alpha=0.1, col="#E2E2E2") 
  plot3d(acicula, soma=F, lwd=2, add=T, alpha=1, col="grey70")
  par3d(zoom=0.52)
  nview3d("frontal", extramat=rotationMatrix(0.2, 1, 0.1, 0.5))
  #z-axis clip
  #clipplanes3d(0, 0, -1, 65000)
  #y-axis clip
  clipplanes3d(1, 0, 0.16, 7000)
  #x-axis clip
  clipplanes3d(0, -1, 0.16, 130000)
}

plot_background_ventral <- function(x){
  nopen3d() # opens a pannable 3d window
  par3d(windowRect = c(0, 0, 200, 200)) #resize for frontal view
  plot3d(bounding_dots, add=T, col="white") 
  plot3d(yolk, add=T, alpha=0.1, col="#E2E2E2") 
  plot3d(acicula, soma=F, lwd=2, add=T, alpha=1, col="grey70")
  par3d(zoom=0.6)
  nview3d('ventral', extramat=(rotationMatrix(0.35, 1, 0, 0)%*%rotationMatrix(0.05, 0, 0, 1)))
  #y-axis clip
  clipplanes3d(1, 0, 0.16, 7000)
  #x-axis clip
  clipplanes3d(0, -1, 0.16, 130000)
}

@@

#load anatomy landmarks
bounding_dots = nlapply(read.neurons.catmaid("^bounding_dots$", pid=11),
                          function(x) smooth_neuron(x, sigma=6000))
yolk <- catmaid_get_volume(4, rval = c("mesh3d", "catmaidmesh", "raw"),
                             invertFaces = T, conn = NULL, pid = 11)
acicula <-   nlapply(read.neurons.catmaid("^acicula$", pid=11),
                       function(x) smooth_neuron(x, sigma=6000))

@@

#function to plot rgl widget with neuron
plot_cell_rgl <- function(annotation, type_of_cell, background){
  ID <- celltypes |>
    filter(`Sensory/inter/motor neuron` == type_of_cell) |> 
    filter(`CATMAID annotation` == annotation) |> 
    pull(`CATMAID annotation`)

  neuron1 = nlapply(read.neurons.catmaid(ID, pid=11),
                    function(x) smooth_neuron(x, sigma=6000))
  if(background == "ventral"){
    plot_background_ventral()
  }
  else{
    plot_background()
  }
  plot3d(neuron1, WithConnectors = F, soma=TRUE, lwd=3,
         add=T, alpha=0.7, col="#0072B2")

  s <- scene3d()
  rglwidget(s, width = 400, height = 100)
}

@@

```{r}
#| echo: false
# PRC
annot <- "celltype1"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# eyespot-PRCR3
annot <- "celltype33"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# eyespot-PRCR1
annot <- "celltype34"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# cPRC
annot <- "celltype5"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# hCR
annot <- "celltype100"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# ventralpygCR
annot <- "celltype101"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")

widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# doCRunp
annot <- "celltype102"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype88")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype89")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype90")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype91")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype92")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype93")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype94")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype95")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype96")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype97")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype88-98
annot <- ("celltype98")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PB neurons celltype80 and 54
annot <- ("celltype80")
plot_cell_name(annot, "Sensory neuron Interneuron")
plot_cell_chars(annot, "Sensory neuron Interneuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron Interneuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PB neurons celltype80 and 54
annot <- ("celltype54")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

### Chemoreceptors

@@

# PU neurons celltype13-15
annot <- ("celltype13")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype13-15
annot <- ("celltype14")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

# PU neurons celltype13-15
annot <- ("celltype15")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

```{r}
#| echo: false
#SNgolden
annot <- ("celltype16")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

```{r}
#| echo: false
#SNhorn
annot <- ("celltype17")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

```{r}
#| echo: false
#SNhook
annot <- ("celltype18")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

```{r}
#| echo: false
#SNlasso
annot <- ("celltype20")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

@@

```{r}
#| echo: false
#SNMIP-vc
annot <- ("celltype24")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)

>>>>

@@

@@

@@

```{r}
#| echo: false
# PRC
annot <- "celltype1"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# eyespot-PRCR3
annot <- "celltype33"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# eyespot-PRCR1
annot <- "celltype34"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# cPRC
annot <- "celltype5"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# hCR
annot <- "celltype100"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# ventralpygCR
annot <- "celltype101"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# doCRunp
annot <- "celltype102"
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
annot <- ("celltype88")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
annot <- ("celltype89")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
#VentraltrunkPUunp
annot <- ("celltype90")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
annot <- ("celltype91")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
#hPUc1
annot <- ("celltype92")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
annot <- ("celltype93")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
annot <- ("celltype94")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
annot <- ("celltype95")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
annot <- ("celltype96")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
annot <- ("celltype97")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype88-98
annot <- ("celltype98")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PB neurons celltype80 and 54
annot <- ("celltype80")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PB neurons celltype80 and 54
#pygPBunp
annot <- ("celltype54")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

#### Flow-sensory MS neurons

@@

# MS neurons celltype35-38
annot <- ("celltype35")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype35.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype35.html){target="_blank"}

# MS neurons celltype35-38
annot <- ("celltype36")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype36.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype36.html){target="_blank"}

# MS neurons celltype35-38
annot <- ("celltype37")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype37.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype37.html){target="_blank"}

# MS neurons celltype35-38
annot <- ("celltype38")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype38.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype38.html){target="_blank"}

#### Chaetal mechanosensory neurons

# chaeMech
annot <- ("celltype71")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype71.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype71.html){target="_blank"}

#### Other putative mechanosensory neurons in the mechanosensory girdle

```{r}
#| echo: false
#SNantlerPDF
annot <- ("celltype26")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#SNblunt
annot <- ("celltype148")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype148.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype148.html){target="_blank"}

```{r}
#| echo: false
#SNbronto
annot <- ("celltype168")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype168.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype168.html){target="_blank"}

```{r}
#| echo: false
#SNFVa
annot <- ("celltype143")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype143.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype143.html){target="_blank"}

```{r}
#| echo: false
#SNPDF-pyg
annot <- ("celltype115")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype115.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype115.html){target="_blank"}

```{r}
#| echo: false
#SNpygM
annot <- ("celltype170")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype170.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype170.html){target="_blank"}

### Nuchal organ chemoreceptors

# PU neurons celltype13-15
annot <- ("celltype13")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype13-15
annot <- ("celltype14")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

# PU neurons celltype13-15
annot <- ("celltype15")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

### Mushroom body sensory cells

```{r}
#| echo: false
#SNtrpa
annot <- ("celltype190")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype190.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype190.html){target="_blank"}

```{r}
#| echo: false
#SNtorii
annot <- ("celltype187")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype187.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype187.html){target="_blank"}

```{r}
#| echo: false
#SNmus
annot <- ("celltype25")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SNMB2
annot <- ("celltype32")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#SNlasso
annot <- ("celltype20")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#SNhorn
annot <- ("celltype17")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#SNhook
annot <- ("celltype18")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#SNgolden
annot <- ("celltype16")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

```{r}
#| echo: false
#SN-NS27
annot <- ("celltype137")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

![](snapshots/celltype137.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype137.html){target="_blank"}

```{r}
#| echo: false
#SN-NS19
annot <- ("celltype133")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

![](snapshots/celltype133.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype133.html){target="_blank"}

```{r}
#| echo: false
#SN-NS18
annot <- ("celltype138")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

@@

![](snapshots/celltype138.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype138.html){target="_blank"}

```{r}
#| echo: false
#SN-NS17
annot <- ("celltype131")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype131.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype131.html){target="_blank"}

```{r}
#| echo: false
#SN-NS1
annot <- ("celltype110")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype110.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype110.html){target="_blank"}

### Apical organ sensory cells

```{r}
#| echo: false
#	SNadNS22
annot <- ("celltype141")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype141.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype141.html){target="_blank"}

```{r}
#| echo: false
#	SN47Ach
annot <- ("celltype52")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype52.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype52.html){target="_blank"}

```{r}
#| echo: false
#	SN-YF5cil
annot <- ("celltype132")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype132.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype132.html){target="_blank"}

```{r}
#| echo: false
#	SN47Ach
annot <- ("celltype52")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype52.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype52.html){target="_blank"}

```{r}
#| echo: false
#	SN-WLD
annot <- ("celltype48")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-NS6
annot <- ("celltype135")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype135.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype135.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS5
annot <- ("celltype130")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype130.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype130.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS4
annot <- ("celltype112")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype112.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype112.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS3
annot <- ("celltype111")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype111.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype111.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS29
annot <- ("celltype136")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype136.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype136.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS22
annot <- ("celltype129")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype129.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype129.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS20
annot <- ("celltype134")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype134.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype134.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS16
annot <- ("celltype139")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype139.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype139.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS15
annot <- ("celltype113")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype113.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype113.html){target="_blank"}

```{r}
#| echo: false
#	SN-MIP4
annot <- ("celltype45")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-MIP1
annot <- ("celltype46")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-IRP2-FMRF
annot <- ("celltype44")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-IRP2-burs
annot <- ("celltype43")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-ASTC
annot <- ("celltype39")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

See also @sec-cPRC for the apical organ ciliary photoreceptors.

### Dorsolateral sensory organ sensory cells

```{r}
#| echo: false
#	SN0DLSO1.2-4
annot <- ("celltype28")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-DLSO3-PDF
annot <- ("celltype40")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-DLSO3
annot <- ("celltype41")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-DLSO2
annot <- ("celltype31")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-DLSO1.3
annot <- ("celltype163")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

![](snapshots/celltype163.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype163.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.2-3
annot <- ("celltype29")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")

```{r}
#| echo: false
#	SN-DLSO1.2-1
annot <- ("celltype30")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
